### 2012-06-30 3.tex
Feverish writing on chapters 2-4

%\chapter{Static and derived phonotactic constraints in Turkish} 
\label{turkish}

@@

This is a principled null hypothesis, but one which can be quickly rejected. \citeauthor{Chomsky1965} point to robust contrasts between equally unattested items like *\emph{blick}, which is recognized by speakers a possible word of English, and *\emph{bnick}, which is not.\footnote{Any readers who are skeptical that \citeauthor{Chomsky1965}'s intuitions generalize will find support for their claim in the wordlikeness judgement data reported in Appendix \ref{albright}.}
%As a quick validation of this claim, consider the results reported by \citet{Albright2007} and discussed in the previous chapter. English speakers asked to rate non-words on a scale from 1-7, where 7 indicates ``most like English'', favor non-words [blʌs, blɑd] (average scores 4.67 and 5.13) over [bnʌs, bnɑd] (average scores 2.06, 2.00).
This preference must be regarded as a learned behavior, since many languages permit  \emph{bn} onsets (e.g., Moroccan Arabic \emph{bni} `building', \emph{bnat} `daughters', \emph{bniqa} `closet'). It is also possible to show speakers access this knowledge not just in wordlikeness judgement tasks but also in naturalistic and quotidien tasks like segmenting spontaneous speech into words, as \citet{McQueen1998} and \citet{Mattys2001b} argue for adult and infant subjects, respectively.

@@

\begin{example}
Turkish vowel features:

\vspace{0.5\baselineskip}
\begin{tabular}{c | c c c c}
                       & \multicolumn{2}{c}{[$-$\textsc{Back}]} & \multicolumn{2}{c}{[$+$\textsc{Back}]} \\
                       & [$-$\textsc{Round}] & [$+$\textsc{Round}] & [$-$\textsc{Round}] & [$+$\textsc{Round}] \\ \midrule
\buf[$+$\textsc{High}] & {i} & {ü} [y] & {ı} [ɯ] & {u} \\
\buf[$-$\textsc{High}] & {e} & {ö} [ø] & {a} [ɑ] & {o} \\
\end{tabular}
\end{example}

@@

%\citep[after][229]{Clements1982}: \\
\begin{example}
\textsc{Backness Harmony}:

\xymatrix@R=24pt@C=24pt{
\txt{V}                                        & \txt{C$_0$~~~~~} & \txt{V} & \txt{(condition: rightward application)} \\
\txt{[α \textsc{Back}]}\ar@{-}[u]\ar@{--}[urr] \\
}
\end{example}

@@

\begin{example}
\label{turknom}
The Turkish nominative:

%\vspace{0.5\baselineskip}
\begin{tabular}{l l l l l}
   & \emph{nom.sg.} & \emph{nom.pl.} \\
a. & ip             & ipler          & `rope' & \citep[][216]{Clements1982} \\
   & el             & eller          & `hand'    \\
   & köy            & köyler         & `village' \\
   & yüz            & yüzler         & `face'    \\
   & kız            & kizlar         & `girl'    \\
   & sap            & saplar         & `stalk'   \\
   & son            & sonlar         & `end'     \\
   & pul            & pullar         & `stamp'   \\
b. & neden          & nedenler       & `reason'  & (TELL) \\ % front
   & kiler          & kilerler       & `pantry'           \\ % front
   & pelür          & pelürler       & `tissue paper'     \\ % back
   & boğaz          & boğazlar       & `throat'           \\ % back
   & sapık          & sapıklar       & `pervert'          \\ % back
\end{tabular}
\end{example}

@@

\begin{example}
\label{turkexcept}
Exceptional Turkish nominatives:

%\vspace{0.5\baselineskip}
\begin{tabular}{l l l l l}
   & \emph{nom.sg.} & \emph{nom.pl.} \\
a. & mezar          & mezarlar       & `grave' & \citep{TELL} \\
   & model          & modeller       & `model' \\
   & silah          & silahlar       & `weapon'     \\
   & memur          & memurlar       & `bureaucrat' \\
   & sabun          & sabunlar       & `soap'       \\
b. & saat           & saatler        & `hour, clock' \\
   & harf           & harfler        & `(alphabetic) letter' \\ %& \citep{Goksel2005}
   & etol           & etoller        & `fur stole' \\
\end{tabular}
\end{example}

@@

\begin{example}
\label{spec}
Underspecification in harmonic roots (after \citealp{Clements1982}):

%\vspace{0.5\baselineskip}
\xymatrix@R=24pt@C=24pt{
\txt{a.} & \txt{harmonic root:~~~~} & \txt{C} & \txt{V} & \txt{C} & \txt{V} \\
&   &    & \txt{[$-$\textsc{Back}]}\ar@{-}[u]\ar@{--}[urr] \\
\txt{b.} & \txt{disharmonic root:} & \txt{C} & \txt{V} & \txt{C} & \txt{V} \\
    &    &         & \txt{[$-$\textsc{Back}]}\ar@{-}[u] & & \txt{[$+$\textsc{Back}]}\ar@{-}[u]
}
\end{example}

@@

Several independent pieces of external evidence argue that this is not the case for root harmony in Turkish. 
The adaptation of non-native word-initial onset clusters, discussed by \citet{Clements1982} and \citet{Kaun1999}, is one such case.\footnote{Thanks to Kie Zuraw for bringing this data to my attention.} While some speakers are said to be capable of pronouncing these non-native clusters, in normal speech the cluster is resolved by epenthesis of a [$+$\textsc{High}] vowel. In most cases, the epenthetic vowel matches the following root vowel for backness, suggesting that adapt foreign words in a way that conforms to the root harmony generalization.

@@

\begin{example}
Adaptation of initial foreign clusters \citep[][247]{Clements1982}:

%\vspace{0.5\baselineskip}
\begin{tabular}{l l l l l l}
a. & spiker  & \alt{} & sipiker  & `announcer' \\
   & fren    & \alt{} & firen    & `break'     \\
b. & brom    & \alt{} & burom    & `bromide'   \\
   & prusya  & \alt{} & purusya  & `Prussia'   \\
%b. & grip    & \alt{} & gırip    & `grippe'    \\ % unexpectedly back
%   & kredi   & \alt{} & kıredi   & `credit'    \\
%   & trablus & \alt{} & tırablus & `Tripoli'   \\
%b. & kral    & \alt{} & kıral    & `king'      \\
%   & grup    & \alt{} & gurup    & `group'     \\
\end{tabular}
\end{example}

@@

\begin{example}
\label{redupgame}
Turkish reduplication game \citep[][231]{Harrison2001}:

\vspace{0.5\baselineskip}
\begin{tabular}{l l l l}
a. & kibrit & kibrit-\{kabrıt\} & `match'    \\
   & bütün  & bütün-\{batın\}   & `whole'    \\
b. & mali   & mali-\{muli\}     & `Mali'     \\
   & butik  & butik-\{batik\}   & `boutique' \\
\end{tabular}
\end{example}

@@

A number of studies on Finnish suggest that speakers of that language, which has a vowel harmony system similar to that of Turkish, make use of (dis)harmony to processing running speech.\footnote{Thanks to Charles Yang for bringing these studies to my attention.} \citet{Suomi1997} and \citet{Vroomen1998} generate nonce trisyllabic words by adding a monosyllabic pseudo-prefix to real and nonce disyllabic words, all of which conform to backness harmony. These stimuli are auditorily presented to subjects who are asked to press a button when the nonce trisyllable ends with a target nonce disyllable, or a real disyllabic word. Speakers are quicker to press the button when the prefix and disyllabic word have different backness specifications. These results suggest that speakers are attuned to the fact that disharmonic transisitions are good predictors of word boundaries. If speakers have also internalized the converse generalization, that harmonic transistions are more likely to be root-internal, then there is additional evidence that harmony is active not just in Finnish affix alternations but also in roots.

@@

\begin{example}
\textsc{Roundness Harmony}:

\xymatrix@R=24pt@C=24pt{
\txt{[α \textsc{Round}]}\ar@{-}[d]\ar@{--}[drr] &             & \txt{[$+$\textsc{High}]} \\
\txt{V}                                         & \txt{C$_0$} & \txt{V}\ar@{-}[u] \\
}
\end{example}

@@

\begin{example}
Turkish nominal suffix allomorphy:

%\vspace{0.5\baselineskip}
\begin{tabular}{l l l l l l l}
   & \emph{nom.sg.} & \emph{dat.sg.} & \emph{gen.sg.}  \\
a. & ip             & ipi            & ipin           & `rope' & \citep[][216]{Clements1982} \\
   & el             & eli            & elin           & `hand'    \\
   & kız            & kızı           & kızın          & `girl'    \\
   & sap            & sapı           & sapın          & `stalk'   \\
   & yüz            & yüzü           & yüzün          & `face'    \\
   & köy            & köyü           & köyün          & `village' \\
   & pul            & pulu           & pulun          & `stamp'   \\
   & son            & sonu           & sonun          & `end'     \\
b. & boğaz          & boğazı         & boğazın        & `throat'  & (TELL) \\
   & pelür          & pelürü         & pelürün        & `tissue paper' \\
   & döviz          & dövizi         & dövizin        & `currency' \\
   & yamuk          & yamuğu         & yamuğun        & `trapezoid' \\
   & ümit           & ümiti          & ümitin         & `hope'     \\
\end{tabular}
\end{example}

@@

\begin{example}
\textsc{Labial Attraction}: %(after \citealt[][286]{Lees1966b}, \citealt[][171]{Inkelas2001}):

\xymatrix@R=24pt@C=8pt{
\txt{[$-$\textsc{Round}]} &                                         & \txt{[$-$\textsc{High}]} & \txt{[$+$\textsc{Labial}]}    & \txt{[$+$\textsc{High}]}\ar@{-}[dr] &         & \txt{[$+$\textsc{Round}]}\ar@{--}[dl] \\
%                         & \txt{V}\ar@{-}[ul]\ar@{-}[ur]\ar@{-}[d] &                           & \txt{C}\ar@{-}[u] &                                      & \txt{V} & \\
                         & \txt{V}\ar@{-}[ul]\ar@{-}[ur]\ar@{-}[d] &                           & \txt{C$_0$ C C$_0$}\ar@{-}[u] &                                      & \txt{V} & \\
                         & \txt{[$+$\textsc{Back}]}\ar@{-}[urrrr]
}
\end{example}

@@

\begin{quote}
\ldots decisive evidence against a rule of Labial Attraction is the existence of a further, much larger set of roots containing /\ldots~aCu~\ldots/ sequences in which the intervening consonant or consonant cluster does not contain a labial\ldots We conclude that there is no systematic restriction on the set of consonants that may occur medially in rotos of the form /\ldots~aCu~\ldots/. \citep[][225]{Clements1982}
\end{quote}

@@

\begin{example}
$\displaystyle \gamma = \frac{C - D}{C + D}$
\end{example}

@@

\begin{example}[Backness harmony wordlikeness forced choices (\citealp{Zimmer1967}:314)]
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{harmonic} & \multicolumn{2}{l}{disharmonic} \\
\midrule
pemez & 30                   & pemaz & 2  \\
tipez & 24                   & tipaz & 8  \\ 
terüz & 19                   & teruz & 13 \\ % roundness violator
teriz & 28                   & terız & 3  \\
tokaz & 26                   & tokez & 6  \\ % roundness violator
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}[Wordlikeness comparisons, roundness harmony]
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{harmonic} & \multicolumn{2}{l}{disharmonic} \\
\midrule
pörüz & 32 & pöriz & 0  \\
tatız & 20 & tatuz & 12 \\
tüpüz & 31 & tüpiz & 1  \\
takız & 22 & takuz & 10 \\
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}[Wordlikeness comparisons]
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{aPu} & \multicolumn{2}{l}{aPı} \\
\midrule
pamuz & 17              & pamız & 15 \\
tafuz & 21              & tafız & 11 \\
tapuz & 17              & tapız & 15 \\
mavuz & 16              & mavız & 16 \\
tabuz & 16              & tabız & 16 \\
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}[Arabic stative verbs]
\begin{tabular}{l l l l}
kabiːr  & `big'        & kabura  & `become big'       \\
ħasan   & `handsome'   & ħasuna  & `become beautiful' \\
dʒadiːb & `barren'     & dʒaduba & `become dry'       \\
\end{tabular}
%b. & saʁiir & }`become small'     & (cf. \emph{saʁiːr} `small') \\
\end{example}

@@

\begin{example}[\textsc{Labial harmony} and etymology in TELL \citealp{Inkelas2001}:187]
\begin{tabular}{l r r r}
        & aPu & aPı & $p$-value \\
Native  & 12  & 11  & \multirow{2}{*}{0.042} \\
Foreign & 84  & 28  \\
\end{tabular}
\end{example}

@@

@@

@@

>>>>

\chapter{Static and derived phonotactic preferences in Turkish}

@@

This is a principled null hypothesis, but one which can be quickly rejected. \citeauthor{Chomsky1965} point to robust contrasts between equally unattested items like *\emph{blick}, which is recognized by speakers a possible word of English, and *\emph{bnick}, which is not.
This preference must be regarded as a learned behavior, since many languages permit  \emph{bn} onsets (e.g., Moroccan Arabic \emph{bni} `building', \emph{bnat} `daughters', \emph{bniqa} `closet'). It is also possible to show speakers access this knowledge not just in wordlikeness judgement tasks but also in naturalistic and quotidien tasks like segmenting spontaneous speech into words, as \citet{McQueen1998} and \citet{Mattys2001b} argue for adult and infant subjects, respectively.

@@

\begin{example}[Turkish vowel features]
\begin{tabular}{c | c c c c}
                       & \multicolumn{2}{c}{[$-$\textsc{Back}]} & \multicolumn{2}{c}{[$+$\textsc{Back}]} \\
                       & [$-$\textsc{Round}] & [$+$\textsc{Round}] & [$-$\textsc{Round}] & [$+$\textsc{Round}] \\ \midrule
\buf[$+$\textsc{High}] & \emph{i} & \emph{ü} [y] & \emph{ı} [ɯ] & \emph{u} \\
\buf[$-$\textsc{High}] & \emph{e} & \emph{ö} [ø] & \emph{a} [ɑ] & \emph{o} \\
\end{tabular}
\end{example}

@@

%\citep[after][229]{Clements1982}: \\
\begin{example}[\textsc{Backness Harmony}]
\xymatrix@R=24pt@C=24pt{
\txt{V}                                        & \txt{C$_0$~~~~~} & \txt{V} & \txt{(condition: rightward application)} \\
\txt{[α \textsc{Back}]}\ar@{-}[u]\ar@{--}[urr] \\
}
\end{example}

@@

\begin{example}[The Turkish nominative] \label{turknom}
\begin{tabular}{l l l l l}
   & nom.sg.      & nom.pl. \\
a. & \emph{ip}    & \emph{ipler}    & `rope'        & \citep[][216]{Clements1982} \\
   & \emph{el}    & \emph{eller}    & `hand'    \\
   & \emph{köy}   & \emph{köyler}   & `village' \\
   & \emph{yüz}   & \emph{yüzler}   & `face'    \\
   & \emph{kız}   & \emph{kızlar}   & `girl'    \\
   & \emph{sap}   & \emph{saplar}   & `stalk'   \\
   & \emph{son}   & \emph{sonlar}   & `end'     \\
   & \emph{pul}   & \emph{pullar}   & `stamp'   \\
b. & \emph{neden} & \emph{nedenler} & `reason'       & (TELL) \\ % front
   & \emph{kiler} & \emph{kilerler} & `pantry'       \\ % front
   & \emph{pelür} & \emph{pelürler} & `tissue paper' \\ % back
   & \emph{boğaz} & \emph{boğazlar} & `throat'       \\ % back
   & \emph{sapık} & \emph{sapıklar} & `pervert'      \\ % back
\end{tabular}
\end{example}

@@

\begin{example}[Exceptional Turkish nominatives] \label{turkexcept}
\begin{tabular}{l l l l l}
   & {nom.sg.}    & {nom.pl.} \\
a. & \emph{mezar} & \emph{mezarlar} & `grave' & \citep{TELL} \\
   & \emph{model} & \emph{modeller} & `model' \\
   & \emph{silah} & \emph{silahlar} & `weapon'     \\
   & \emph{memur} & \emph{memurlar} & `bureaucrat' \\
   & \emph{sabun} & \emph{sabunlar} & `soap'       \\
b. & \emph{saat}  & \emph{saatler}  & `hour, clock' \\
   & \emph{harf}  & \emph{harfler}  & `(alphabetic) letter' \\ %& \citep{Goksel2005}
   & \emph{etol}  & \emph{etoller}  & `fur stole' \\
\end{tabular}
\end{example}

@@

\begin{example}[Underspecification in harmonic roots (after \citealp{Clements1982})] \label{spec}
\xymatrix@R=24pt@C=24pt{
\txt{a.} & \txt{harmonic root:~~~~} & \txt{C} & \txt{V} & \txt{C} & \txt{V} & \txt{\ldots} \\
&   &    & \txt{[$-$\textsc{Back}]}\ar@{-}[u]\ar@{--}[urr] \\
\txt{b.} & \txt{disharmonic root:} & \txt{C} & \txt{V} & \txt{C} & \txt{V} & \txt{\ldots} \\
    &    &         & \txt{[$-$\textsc{Back}]}\ar@{-}[u] & & \txt{[$+$\textsc{Back}]}\ar@{-}[u]
}
\end{example}

@@

Several independent pieces of external evidence argue that this is not the case for root harmony in Turkish. 
The adaptation of non-native word-initial onset clusters, discussed by \citet{Clements1982} and \citet{Kaun1999}, is one such case.\footnote{Thanks to Kie Zuraw for bringing this data to my attention.} While some speakers are said to be capable of pronouncing these non-native clusters, in normal speech the cluster is resolved by epenthesis of a [$+$\textsc{High}] vowel. In most cases, the epenthetic vowel matches the following root vowel for backness, suggesting that adapt foreign words in a way that conforms to the root harmony generalization.\footnote{At the same time, this shows that adaptation is not simply applying rules, like \textsc{Backness Harmony}, to foreign forms. Rather, foreign forms are restructured as non-exceptional Turkish lexical items.}

@@

\begin{example}[Adaptation of initial foreign clusters (\citealp{Clements1982}:247)] 
\begin{tabular}{l l l l l l}
a. & \emph{spiker}  & \alt{} & \emph{sipiker}  & `announcer' \\
   & \emph{fren}    & \alt{} & \emph{firen}    & `break'     \\
b. & \emph{brom}    & \alt{} & \emph{burom}    & `bromide'   \\
   & \emph{prusya}  & \alt{} & \emph{purusya}  & `Prussia'   \\
%b. & grip    & \alt{} & gırip    & `grippe'    \\ % unexpectedly back
%   & kredi   & \alt{} & kıredi   & `credit'    \\
%   & trablus & \alt{} & tırablus & `Tripoli'   \\
%b. & kral    & \alt{} & kıral    & `king'      \\
%   & grup    & \alt{} & gurup    & `group'     \\
\end{tabular}
\end{example}

@@

\begin{example}[Turkish reduplication game (\citealp{Harrison2001}:231)] \label{redupgame}
\begin{tabular}{l l l l}
a. & \emph{kibrit} & \emph{kibrit}-\{\emph{kabrıt}\} & `match'    \\
   & \emph{bütün}  & \emph{bütün}-\{\emph{batın}\}   & `whole'    \\
b. & \emph{mali}   & \emph{mali}-\{\emph{muli}\}     & `Mali'     \\
   & \emph{butik}  & \emph{butik}-\{\emph{batik}\}   & `boutique' \\
\end{tabular}
\end{example}

@@

\label{harmonyandsegmentation} A number of studies on Finnish suggest that speakers of that language, which has a vowel harmony system similar to that of Turkish, make use of (dis)harmony to processing running speech.\footnote{Thanks to Charles Yang for bringing these studies to my attention.} \citet{Suomi1997} and \citet{Vroomen1998} generate nonce trisyllabic words by adding a monosyllabic pseudo-prefix to real and nonce disyllabic words, all of which conform to backness harmony. These stimuli are auditorily presented to subjects who are asked to press a button when the nonce trisyllable ends with a target nonce disyllable, or a real disyllabic word. Speakers are quicker to press the button when the prefix and disyllabic word have different backness specifications. These results suggest that speakers are attuned to the fact that disharmonic transisitions are good predictors of word boundaries. If speakers have also internalized the converse generalization, that harmonic transistions are more likely to be root-internal, then there is additional evidence that harmony is active not just in Finnish affix alternations but also in roots.

@@

\begin{example}[\textsc{Roundness Harmony}]
\xymatrix@R=24pt@C=24pt{
\txt{[α \textsc{Round}]}\ar@{-}[d]\ar@{--}[drr] &             & \txt{[$+$\textsc{High}]} \\
\txt{V}                                         & \txt{C$_0$} & \txt{V}\ar@{-}[u] \\
}
\end{example}

@@

\begin{example}[Turkish nominal suffix allomorphy]
\begin{tabular}{l l l l l l l}
   & {nom.sg.}    & {dat.sg.}     & {gen.sg.}  \\
a. & \emph{ip}    & \emph{ipi}    & \emph{ipin}    & `rope' & \citep[][216]{Clements1982} \\
   & \emph{el}    & \emph{eli}    & \emph{elin}    & `hand'    \\
   & \emph{kız}   & \emph{kızı}   & \emph{kızın}   & `girl'    \\
   & \emph{sap}   & \emph{sapı}   & \emph{sapın}   & `stalk'   \\
   & \emph{yüz}   & \emph{yüzü}   & \emph{yüzün}   & `face'    \\
   & \emph{köy}   & \emph{köyü}   & \emph{köyün}   & `village' \\
   & \emph{pul}   & \emph{pulu}   & \emph{pulun}   & `stamp'   \\
   & \emph{son}   & \emph{sonu}   & \emph{sonun}   & `end'     \\
b. & \emph{boğaz} & \emph{boğazı} & \emph{boğazın} & `throat'  & (TELL) \\
   & \emph{pelür} & \emph{pelürü} & \emph{pelürün} & `tissue paper' \\
   & \emph{döviz} & \emph{dövizi} & \emph{dövizin} & `currency' \\
   & \emph{yamuk} & \emph{yamuğu} & \emph{yamuğun} & `trapezoid' \\
   & \emph{ümit}  & \emph{ümiti}  & \emph{ümitin}  & `hope'     \\
\end{tabular}
\end{example}

@@

\begin{example}[\textsc{Labial Attraction}]
%(after \citealt[][286]{Lees1966b}, \citealt[][171]{Inkelas2001}): 
\xymatrix@R=24pt@C=8pt{
\txt{[$-$\textsc{Round}]} &                                         & \txt{[$-$\textsc{High}]} & \txt{[$+$\textsc{Labial}]}    & \txt{[$+$\textsc{High}]}\ar@{-}[dr] &         & \txt{[$+$\textsc{Round}]}\ar@{--}[dl] \\
%                         & \txt{V}\ar@{-}[ul]\ar@{-}[ur]\ar@{-}[d] &                           & \txt{C}\ar@{-}[u] &                                      & \txt{V} & \\
                         & \txt{V}\ar@{-}[ul]\ar@{-}[ur]\ar@{-}[d] &                           & \txt{C$_0$ C C$_0$}\ar@{-}[u] &                                      & \txt{V} & \\
                         & \txt{[$+$\textsc{Back}]}\ar@{-}[urrrr]
}
\end{example}

@@

\begin{quote}
\ldots{}decisive evidence against a rule of Labial Attraction is the existence of a further, much larger set of roots containing /\ldots~aCu~\ldots/ sequences in which the intervening consonant or consonant cluster does not contain a labial\ldots We conclude that there is no systematic restriction on the set of consonants that may occur medially in roots of the form /\ldots~aCu~\ldots/. \citep[][225]{Clements1982}
\end{quote}

@@

@@

\begin{example}[Backness harmony wordlikeness forced choices (\citealp{Zimmer1969}:314)]
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{harmonic} & \multicolumn{2}{l}{disharmonic} \\
\midrule
\emph{pemez} & 30            & \emph{pemaz} & 2  \\
\emph{tipez} & 24            & \emph{tipaz} & 8  \\ 
\emph{terüz} & 19            & \emph{teruz} & 13 \\ % roundness violator
\emph{teriz} & 28            & \emph{terız} & 3  \\
\emph{tokaz} & 26            & \emph{tokez} & 6  \\ % roundness violator
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}[Wordlikeness comparisons, roundness harmony]
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{harmonic} & \multicolumn{2}{l}{disharmonic} \\
\midrule
\emph{pörüz} & 32            & \emph{pöriz} & 0  \\
\emph{tatız} & 20            & \emph{tatuz} & 12 \\
\emph{tüpüz} & 31            & \emph{tüpiz} & 1  \\
\emph{takız} & 22            & \emph{takuz} & 10 \\
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}[Wordlikeness comparisons]
\begin{tabular}{l r l r}
\toprule
\multicolumn{2}{l}{\emph{a}P\emph{u}} & \multicolumn{2}{l}{\emph{a}P\emph{ı}} \\
\midrule
\emph{pamuz} & 17       & \emph{pamız} & 15 \\
\emph{tafuz} & 21       & \emph{tafız} & 11 \\
\emph{tapuz} & 17       & \emph{tapız} & 15 \\
\emph{mavuz} & 16       & \emph{mavız} & 16 \\
\emph{tabuz} & 16       & \emph{tabız} & 16 \\
\bottomrule
\end{tabular}
\end{example}

@@

\begin{example}[Arabic stative verbs]
\begin{tabular}{l l l l}
\hspace{0pt}[kabiːr]  & `big'      & [kabura]  & `become big'       \\
\hspace{0pt}[ħasan]   & `handsome' & [ħasuna]  & `become beautiful' \\
\hspace{0pt}[dʒadiːb] & `barren'   & [dʒaduba] & `become dry'       \\
\end{tabular}
%b. & saʁiir & }`become small'     & (cf. \emph{saʁiːr} `small') \\
\end{example}

@@

\begin{example}[\textsc{Labial harmony} and etymology in TELL \citealp{Inkelas2001}:187]
\begin{tabular}{l r r r}
        & \emph{a}P\emph{u} & \emph{a}P\emph{ı} & $p$-value \\
Native  & 12                & 11                & \multirow{2}{*}{0.042} \\
Foreign & 84                & 28                \\
\end{tabular}
\end{example}

@@

%It is important to note that the nature of the \emph{blick}/\emph{bnick} contrast is no longer a mystery. 
%Generative phonological theory at the time of \emph{SPE} lacked the representational vocabulary to directly distinguish between word-initial /bn/, which is disallowed, and /bn/ as a licit syllable contact cluster (e.g., \emph{o}[b.n]\emph{oxious}), a point first made by \citep{Hooper1973}. It is not the introduction of prosodic primitives into generative phonology that explains the contrast between \emph{blick} and \emph{bnick}, though, but rather the principle that surface forms must be syllabified \citep[e.g.,][63f.]{Kiparsky1982b} which \emph{bnick} fails. If, as is standardly assumed, phonology repairs unsyllabifiable outputs \citep[e.g.][]{Ito1989a,Noske1992}, then \emph{bnick} is an impossible output, doomed to be modified (perhaps to \emph{nick}; \citealt[][19f.]{Wolf2009}), and /bnɪk/ is an impossible UR by Stampean occultation. 

@@

%In a wordlikeness task, a speaker is presented with nonce words and asked to report such intuitions about the ``possibility'' of a word. 
%The alternative hypothesis, then, is that a statistically reliable co-occurrence restriction will be reflected in native speakers' wordlikeness judgements. 
%The data below, drawn from Turkish, shows that 

@@

%\begin{unlabeledexample}
%$\displaystyle \gamma = \frac{C - D}{C + D}$
%\end{unlabeledexample}
%\footnote{Any readers who are skeptical that \citeauthor{Chomsky1965}'s intuitions generalize will find support for their claim in the wordlikeness judgement data reported in Appendix \ref{albright}.}
%As a quick validation of this claim, consider the results reported by \citet{Albright2007} and discussed in the previous chapter. English speakers asked to rate non-words on a scale from 1-7, where 7 indicates ``most like English'', favor non-words [blʌs, blɑd] (average scores 4.67 and 5.13) over [bnʌs, bnɑd] (average scores 2.06, 2.00).
